Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
+ comment on the domains of controller/uncertainty
Updated running example in CEGIS.

Essentially, the synthesis problem we are trying to solve is the following:
find a digital controller denoted by  $N_c$ and $D_c$ that
makes the closed-loop system stable 
for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
Note that, similar to the rest of the paper, we use the notation 
$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
$(\Delta N_G, \Delta D_G)$ represents $x$.

%% \red{[clear elucidation of the mapping between this and the domains used 
%% in the general description of the synthesiser]}

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\blue{
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
}
$$

%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

>>>>

Essentially, the synthesis problem we are trying to solve is the following:
find a digital controller denoted by  $N_c$ and $D_c$ that
makes the closed-loop system stable 
for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
Note that, similar to the rest of the paper, we use the notation 
$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
$(\Delta N_G, \Delta D_G)$ represents $x$. 
We compute the controller $(N_c,D_c)$ in the domain 
$\mathbb{R}\langle I,F \rangle$ and 
the uncertainty in $\mathbb{R}\langle I_b,F_b \rangle$.

% \red{[clear elucidation of the mapping between this and the domains used 
% in the general description of the synthesiser]}

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. Back in the {\sc synthesise}
phase, we thus retrieve a candidate solution with all coefficients 0.
The {\sc verify} phase now provides the first counterexample at higher
precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\blue{
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
}
$$

%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
In the next {\sc synthesise} phase, we get a new candidate solution that holds for
the new, higher precision counterexample:
